On Round-Based Games in First-Person-Shooter (FPS) E-Sports

### 2022-07-14 presentation.qmd
make progress on pres

---
title: "Tactical Round-Based Games"
author: "Tony ElHabr"
format:
  revealjs:
    incremental: false
    theme: dark
execute: 
  include: false
  echo: false
---

@@

dir_proj <- '57-cod_snd'

@@

-   Call of Duty League (CDL)
    -   Search and Destroy
-   Valorant Pro League
    -   Plant/Defuse

## How do you win SnD?

Several ways to win a round:

1.  One team eliminate all members of the other team prior to a bomb plant.
2.  The offensive team wins if they eliminate all members of the defensive team after a bomb plant.
3.  The defensive team wins if they defuse the bomb after a bomb plant.[^1]
4.  The defensive team wins if the offensive team does not make a plant by the time the round timer ends.

[^1]: Often the defensive team will try to eliminate all offensive team members prior to making the defuse, but in some cases, they may try to "ninja" defuse.

@@

-   Total series: **`r n_series`**
-   Total rounds: **`r n_rounds`**
-   Offensive win %: **`r offensive_win_pct`**
-   Offensive sides plant %: **`r plant_pct`**
-   Win % when planting: **`r offensive_plant_and_win_pct`**
-   Win % when earning first blood: **`r offensive_first_blood_win_pct`**

@@

![](offensive_win_r1_prop.png)

>>>>

---
title: "On Round-Based Games in First-Person-Shooter (FPS) E-Sports"
author: "Tony ElHabr"
format:
  revealjs:
    incremental: false
    theme: [dark, theme.scss]
execute: 
  include: false
  echo: false
---

@@

@@

-   Call of Duty League (CDL)
    -   Search and Destroy (SnD)
-   Valorant Pro League
    -   Plant/Defuse

## How does a team win a round of SnD?

::: fragment
1.  One team eliminates all members of the other team prior to a bomb plant.
:::

::: fragment
2.  The offensive team eliminates all members of the defensive team after a bomb plant.
:::

::: fragment
3.  The defensive team defuses the bomb after a bomb plant.
:::

::: fragment
Often the defensive team will try to eliminate all offensive team members prior to making the defuse, but in some cases, they may try to "ninja" defuse.
:::

::: fragment
4.  The offensive team does not make a plant by the time the round timer ends.
:::

@@

::: fragment
-   Total series: **`r n_series`**
:::

::: fragment
-   Total rounds: **`r n_rounds`**
:::

::: fragment
-   Offensive sides plant %: **`r plant_pct`**
:::

::: fragment
-   Offensive win %: **`r offensive_win_pct`**
:::

::: fragment
-   Win % when planting: **`r offensive_plant_and_win_pct`**
:::

::: fragment
-   Win % when earning first blood: **`r offensive_first_blood_win_pct`**
:::

@@

![](offensive_win_r1_prop.png){fig-align="center"}
